Untitled

### 2017-08-15 Average local prices.Rmd
New postcodes
New postcodes have been included to make the LSOA matching better.

Also loads more local regions have been added and modelling of the negative positive split.

@@

#Construct a distance network across all the LADs
NetworkDist <- 1:length(V(g1)) %>% 
  map(~{
  bfs(g1, root = .x, unreachable = FALSE, rank = TRUE, dist = TRUE)$rank %>%
      as.matrix %>% t %>% as.data.frame
  }) %>% 
  bind_rows() %>% mutate(LAD11CD = names(.))

@@

LocalMean <- NetworkDist %>% 
  gather(key= "LAD11CD2", value = "distance", -LAD11CD) %>%
  filter(LAD11CD %in% CombineAB$LAD11CD, distance <=3) %>%
#join on the average prices per LAD
  left_join(LADprice, by = c("LAD11CD2"="Admin_district_code")) %>%
  #find local mean
  group_by(LAD11CD) %>%
  summarise(LocalMean = mean(price,na.rm = TRUE))

test <- Combine1ExO2 %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  #filter out wales
  filter(!grepl("W", LAD11CD))%>%
  select(LAD11NM, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value, pricepercent, LAD11CD) %>%
  mutate(outcome = LUPdepExt>Extent)  %>% 
  left_join(LocalMean, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code")) %>%
  mutate(priceRatio = (price/LocalMean)) %>%
  mutate(LUPdepExt.Extent = LUPdepExt-Extent, price.LocalMean = price>LocalMean ) #%>%
#select(LAD11CD, LAD11NM, priceRatio, price, LocalMean, absdiff, Ttest.p.value, maxPerc, LUPdepExt)
#remove barrow
#filter(LAD11CD !="E07000027")

@@

rpart.model <- rpart(as.factor(absdiff>0) ~ maxPerc, test)
rpart.model1 <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
rpart.model2 <- rpart(as.factor(absdiff>0) ~ LUPdepExt.Extent + maxPerc + priceRatio, test)
rpart.model3 <- svm(as.factor(absdiff>0) ~ LUPdepExt+Extent + maxPerc + priceRatio, test, type = "C", kernel = "radial")
rpart.model3 <- svm(as.factor(absdiff>0) ~ maxPerc + LUPdepExt+ Extent, test, type = "C", kernel = "radial")

>>>>

Test on northern Ireland
```{r}

@@

#Construct a distance network across all the LADs
#dist now fixed!
NetworkDist <- 1:length(V(g1)) %>% 
  map(~{
  bfs(g1, root = .x, unreachable = FALSE, rank = TRUE, dist = TRUE)$dist %>%
      as.matrix %>% t %>% as.data.frame
  }) %>% 
  bind_rows() %>% mutate(LAD11CD = names(.))

@@

#three or less distance
LocalMean <- NetworkDist %>% 
  gather(key= "LAD11CD2", value = "distance", -LAD11CD) %>%
  filter(LAD11CD %in% CombineAB$LAD11CD, distance <=4) %>%
#join on the average prices per LAD
  left_join(LADprice, by = c("LAD11CD2"="Admin_district_code")) %>%
  #find local mean
  group_by(LAD11CD) %>%
  summarise(LocalMean = mean(price,na.rm = TRUE))

test <- Combine1ExO2 %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  #filter out wales
  filter(!grepl("W", LAD11CD))%>%
  select(LAD11NM, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value,  LAD11CD) %>%
  mutate(outcome = LUPdepExt>Extent)  %>% 
  left_join(LocalMean, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code")) %>%
  mutate(priceRatio = (price/LocalMean)) %>%
  mutate(LUPdepExt.Extent = LUPdepExt-Extent, price.LocalMean = price-LocalMean ) #%>%
#select(LAD11CD, LAD11NM, priceRatio, price, LocalMean, absdiff, Ttest.p.value, maxPerc, LUPdepExt)
#remove barrow
#filter(LAD11CD !="E07000027")

@@

rpart.model <- rpart(as.factor(absdiff>0) ~ maxPerc, test)
rpart.model1 <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
rpart.model2 <- rpart(as.factor(absdiff>0) ~ LUPdepExt + maxPerc + priceRatio, test)
rpart.model3 <- svm(as.factor(absdiff>0) ~ LUPdepExt+Extent + maxPerc + priceRatio, test, type = "C", kernel = "radial")
rpart.model3 <- svm(as.factor(absdiff>0) ~ maxPerc + LUPdepExt+ Extent, test, type = "C", kernel = "radial")

### 2017-08-15 CreateExcelTemplates.Rmd
New postcodes
New postcodes have been included to make the LSOA matching better.

Also loads more local regions have been added and modelling of the negative positive split.

if(file.exists(file.path(DataFolder,"PstCdLSOA.rds"))){
 PstCdLSOA.raw <- readRDS(file.path(DataFolder,"PstCdLSOA.rds"))
} else {
  source(file.path(CommonCode, "PostcodeLookup.R"))
}

@@

PstCdLSOA[PstCdLSOA$Postcode=="DY4 4BA", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="DY4 0YX", c(3,4,7)] 
PstCdLSOA[PstCdLSOA$Postcode=="DY4 4BB", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="DY4 0YX", c(3,4,7)]

>>>>

if(file.exists(file.path(DataFolder,"PstCdLSOA.rds"))){
PstCdLSOA.raw <- readRDS(file.path(DataFolder,"PstCdLSOA.rds"))
} else {
  PstCdLSOA.raw  <- MatchPostCode2LSOA(file.path(basewd, "ONS postcodes May17", "Data", "CSV"),
                        file.path(basewd, "ONS postcodes May17", "Doc") )
  setwd(DataFolder)
  saveRDS(PstCdLSOA.raw, "PstCdLSOA.rds")
}

@@

PstCdLSOA[PstCdLSOA$Postcode=="DY44BA", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="DY40YX", c(3,4,7)] 
PstCdLSOA[PstCdLSOA$Postcode=="DY44BB", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="DY40YX", c(3,4,7)]

### 2017-08-15 LowUseLondon.Rmd
New postcodes
New postcodes have been included to make the LSOA matching better.

Also loads more local regions have been added and modelling of the negative positive split.

test <-  ls(pattern = "LON") %>% map_df(~eval(parse(text=.x))) %>%
  group_by(Admin_ward_code) %>%
  summarise(LAD11NM = first(LAD11NM),
            MeanPrice = first(MeanPrice),
            WardLowUse = first(WardLowUse)) %>%
  group_by(LAD11NM) %>%
  summarise(totalLow = sum(MeanPrice*WardLowUse)/1e6,
            TotalEmpt = sum(WardLowUse))

sum(test$totalLow, na.rm = T)  
sum(test$TotalEmpt, na.rm = T)  
length(unique(test$LAD11NM))

@@

>>>>

test <-  ls(pattern = "LON") %>% map_df(~eval(parse(text=.x))) %>%
  group_by(Admin_ward_code) %>%
  summarise(LAD11NM = first(LAD11NM),
            MeanPrice = first(MeanPrice),
            WardLowUse = first(WardLowUse),
            WardPop = first(WardPop)) %>%
  group_by(LAD11NM) %>%
  summarise(totalLow = sum(MeanPrice*WardLowUse)/1e6,
            TotalEmpt = sum(WardLowUse),
            TotalPop = sum(WardPop))

#possible extra 8-14 billion more in the remaining boroughs anout 90b total
#poss addition 7k LUPS about 80k total

sum(test$totalLow, na.rm = T)*10^6/  
sum(test$TotalEmpt, na.rm = T)  
sum(test$TotalPop, na.rm = T)  
length(unique(test$LAD11NM))

@@

test <-list( WestminsterLONDATA, ChelseaLONDATA, CoLLONDATA, CamdenLONDATA, LambethLONDATA, SouthwarkLONDATA, HammersmithLONDATA,
             WandsworthLONDDATA) %>%
  bind_rows() %>%
  PlotMap(.,
          title = "Map of London with all current data")

### 2017-08-15 PaperCode.Rmd
New postcodes
New postcodes have been included to make the LSOA matching better.

Also loads more local regions have been added and modelling of the negative positive split.

@@

@@

Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up/Figures"
```

```{r}
source(file.path(CommonCode, "AuxdataLoad.R"))
```

@@

@@

@@

```{r}
BournemouthDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = c(5,11:14,18))

@@

@@

```{r}
#Wiltshire have not included everything
WiltshireDATA <- read_excel("Wiltshire ENQ07536 - Council tax discounts 2.xlsx",
                               sheet=1)[1:4] %>%
  StructureData(lowuse = 3:8)
```

@@

@@

@@

@@

@@

##Durham
```{r}
  DarlingtonDATA <- read_excel("Darlington DBC-0809-17.xlsx" , sheet=1) %>% .[,1:4] %>%
    StructureData()

  HartlepoolData <- read_csv("FOI 7942 HartlepoolDiscountsLSOA.csv") %>% .[,1:4] %>%
    StructureData(2:7)

@@

#Conway have sen the wrong stuff  
# ConwayDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
#   rename(Postcode = geo_postcode) %>%
#   mutate(Postcode = sub(" ", "", Postcode)) %>%
#   left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
#   rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
#   select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
#   StructureData()

@@

#number of LUPS and Total Homes
ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  filter(!is.na(LAD11NM)) %>%
  summarise(
           TotalLads = length(unique(LAD11CD)),
           LowUse = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           PercHomes = Homes/sum(EW2$Homes),
           Population = sum(Pop, na.rm= T),
           Poperc = Population/sum(EW2$Pop))

@@

z<- MakeLeaflet(CeredigionDATA)
z
# 
setwd(basewd)
 saveWidget(z, file=file.path(basewd, "CeredigionDATA.html"), selfcontained = TRUE )

@@

@@

#Repeat excluding all the properties classed as other

BootStrapRESExO <-LoadAddDistribCompare("BootStrapRESExO.rds", 
                                         PropertyTypes = c("D", "S", "T", "F"))

BootStrapRESExOA <-LoadAddDistribCompare("BootStrapRESExOA.rds", type = "A", 
                                         PropertyTypes = c("D", "S", "T", "F"))

BootStrapRESExOB <-LoadAddDistribCompare("BootStrapRESExOB.rds", type = "B", 
                                         PropertyTypes = c("D", "S", "T", "F"))

@@

@@

#This is so cool, Also needs to be discussed in great detail, it is probablu due to the demolition and renovation of council housing
Combine1 %>% ggplot(.,aes(x= absdiff, y = Ttest.p.value)) + geom_point()
Combine2 %>% ggplot(.,aes(x= absdiff, y = Ttest.p.value)) + geom_point()

@@

```{r}
test <- BootStrapRESExO$ChelseaLON %>% 
  group_by(class) %>%
  summarise_all(funs(mean))

test2 <- test %>%
  select(-class) %>%
  summarise_all(funs(sum)) %>%
  mutate(LowUseValue = LowUseValue/1e9)
```

@@

BootStrapRES$CoLLON %>% PlotClassDiff()
BootStrapRESExO$CoLLON %>% PlotClassDiff()
BootStrapRESExOA$CoLLON %>% PlotClassDiff()
BootStrapRESExOB$CoLLON %>% PlotClassDiff()

HouseMatch <- data_frame(PropType = "D,S,T,F,O" %>% str_split(",") %>% unlist,
type = "Detached,Semi-Detached,Terraced,Flats/Maisonettes,Other"%>% str_split(",") %>% unlist)

test <- CoLLONDATA %>% SubsetPrice() %>% left_join(HouseMatch)
testB <- CoLLONDATA %>% SubsetPrice("B") %>% left_join(HouseMatch)
testA <- CoLLONDATA %>% SubsetPrice("A") %>% left_join(HouseMatch)

table(test$type, test$class)
table(testA$type, testA$class)
table(testB$type, testB$class)

CoLnums <- BootStrapRES$CoLLON %>% 
  group_by(class) %>%
  summarise_all(funs(mean(., na.rm = TRUE)))

CoLnumsA <- BootStrapRESA$CoLLON %>% 
  group_by(class) %>%
  summarise_all(funs(mean(., na.rm = TRUE)))

@@

sum(prices$X15 == "B")/nrow(prices)

test <- ABratio4 %>% 
  filter(LAD11CD %in% CurrentLADS)

ABratio3 %>% ggplot(., aes(x = Valueratio)) +geom_density()

@@

CombineAB %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Countratio>0.2)) + geom_point()

CombineAB %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = mean)) + geom_point()

@@

#Look Kings Lynn and harrogate as they are strange results

KingsLynnDep <- KingsLynnDATA %>% left_join(LSOADep, by = "LSOA_CODE") %>% 
  mutate(deprank = rank(Decile..where.1.is.most.deprived.10..of.LSOAs.))

HarrogateDep <- HarrogateDATA %>% left_join(LSOADep, by = "LSOA_CODE") %>%
  mutate(deprank = rank(Decile..where.1.is.most.deprived.10..of.LSOAs.))

@@

test <- KingsLynnDep %>% 
  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))

test <- BromleyLONDATA %>% 
  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))

sum(test$WeightedLUP, na.rm = TRUE)

LUPdepExt <- ls(pattern = "DATA") %>% map_dbl(~{
df <- get(.x)
test <- df %>% 
  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))

@@

LADprice <- prices %>%
  filter(X5!= "O") %>%
  group_by(Admin_district_code) %>%
summarise(price = mean(X2)) %>%
  mutate(meandiff = price-mean(price),
         pricepercent = percent_rank(price))

test <- Combine1ExO2 %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  #filter out wales
  filter(!grepl("W", LAD11CD))%>%
  select(LAD, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value, pricepercent) %>%
  mutate(outcome = LUPdepExt>Extent)

test %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = outcome)) +
  geom_jitter()

svm.model <- svm(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
#why do the two rforest models have such different results
#rpart.model <- randomForest(as.factor((absdiff>0))~ LUPdepExt+ maxPerc, test)
rpart.model <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)

confusionMatrix(predict(svm.model, test, type = class),as.factor(test$absdiff>0))

confusionMatrix( predict(rpart.model, test, type = "class"),as.factor(test$absdiff>0))

@@

@@

@@

Why are some areas with negative difference?

The max percentage of low use is 5%
There is the council estate renovation effect.
All the areas are Urban
Also check deprivation,

sum(Combine1$Ttest.p.value>0.5)/nrow(Combine1)
sum(Combine1$Ttest.p.value>0.5 & Combine1$maxPerc>5)/sum(Combine1$maxPerc>5)

Combine1ExO[Combine1ExO$Ttest.p.value>0.5 & Combine1ExO$maxPerc>5,]
Combine2ExO[Combine2ExO$Ttest.p.value>0.5 & Combine2ExO$maxPerc>5,]
Combine3ExO[Combine3ExO$Ttest.p.value>0.5 & Combine3ExO$maxPerc>5,]

table(Combine2$Ttest.p.value>0.5 & Combine2$maxPerc>5, Combine1$Ttest.p.value>0.5 & Combine1$maxPerc>5)

LADAB <- ChelseaLONDATA%>% SubsetPrice
  table(LADAB$X15, LADAB$class)

Combine1 %>% ggplot(.,aes(x= abs(maxPerc), y = Ttest.p.value)) + geom_point()

#P.value is low if diff perc is over 5%
#Both southwark and Tower of london have concil flat renovation?
#Southwark the Aylesbury estate is being redeveloped making emptyness much higher than expected
#The blackwall an cubitt are being redevleoped with the blackwall reach, some housing is empty others are still occupied demolishin has not occured
Combine1 %>% ggplot(.,aes(x= diffPerc, y = Ttest.p.value)) + geom_point()

Combine1ExO %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value)) + geom_point() +
  labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")

Combine2 %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value)) + geom_point() +
  labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")

#Boring doesn't show anything interesting
Combine1 %>% ggplot(.,aes(x= p.value.x, y = Ttest.p.value, colour =diffPerc>5 )) + geom_point()

Combine1 %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value, colour =absdiff>0 )) + geom_point()

test <- Combine1 %>%
  select(LAD,p.value.x, Ttest.p.value, absdiff , maxPerc, minPerc,diffPerc, skew)

Combine1 %>% ggplot(.,aes(x= skew, y= Ttest.p.value)) + geom_point()

```{r}
test <- Combine1 %>% filter(Ttest.p.value>0.05)
```

>>>>

#ico complaint ref
fs-506-897-47

@@

What's the Deal with Westminster?
Westminsters Data is very low, I want to check what codes are going on.
Westminster
PCLB00: Second home class B/A
PCLB50: 
PCLC00: Empty and unfurnsished
PCLC99: 
PCLD00: Undergoing major repairs
PCLJ50:
Single:

#Setup

@@

Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up/Figures"
source(file.path(CommonCode, "AuxdataLoad.R"))
```

@@

TorbayDATA <- read_excel("Torbay_discounts 1718551.xlsx"  , sheet=1)[1:4] %>%
  StructureData()

MidDevonDATA <- read_excel("MidDevon FOI04942Information 3.xlsx" , sheet=1)[1:4] %>%
  StructureData(c(7,10:11,20:22,26,28))

TorridgeDATA <- read_excel("FOI_TorridgeDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
  StructureData(c(4:5,7:10,13))

@@

MendipDATA <- read_excel("Mendip 356 20170706 Response.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse= c(37:39,52:54,65:66,69))

@@

```{r}
PooleDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = c(5,11:14,18))

@@

WeymouthDATA <-  read_excel("63687 Weymouth and PortlandDiscountsLSOA - 010817.xlsx"    ,
                               sheet=1)[1:4] %>%
  StructureData()

WestDorsetDATA <-  read_excel("47019 West DorsetDiscountsLSOA - 010817.xlsx"     ,
                               sheet=1)[1:4] %>%
  StructureData()

PurbeckDATA <-  read_excel("PurbeckDiscountsLSOA - 010817.xlsx"      ,
                               sheet=1)[1:4] %>%
  StructureData()

@@

```{r}
#Wiltshire have not included everything
WiltshireDATA <- read_excel("Wiltshire ENQ07536 - Council tax discounts 2.xlsx",
                               sheet=1)[1:4] %>%
  StructureData(lowuse = 3:8)

SwindonDATA <- read_excel("Swindon - 7th July 2017 - Part 2 (Discounts).xlsx" ,
                               sheet=1)[1:4] %>%
  StructureData(2:6)
```

@@

IpswichDATA <- read_xlsx("IpswichDiscountsLSOA.xlsx")[1:4] %>%
   StructureData(c(2:4,6:11,13:15))

#Mid Suffolk and Babergh
#These have been combined and are just the postcodes so need to be fixed
#Missing loads of postcodes
MidSuffolkDATA <- read_excel("MidSuffolk FOI MF379 1718 Discount.xlsx") %>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
  StructureData(c(2:12,14:15))

BaberghDATA <- read_excel("Babergh FOI BF378 1718 Discount.xlsx")%>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
  StructureData(c(2:6,8:11,13:15))

@@

CambridgeDATA <- read_excel("566 - Copy of Copy of CambridgeDiscountsLSOA .xlsx" , sheet=1)[1:4] %>%
  StructureData(2:5)

@@

# Middlesbrough sent the wrong data
# MiddlesbroughDATA <- read_excel( "Middlesbrough FOI RES - 011397 Discounts.xlsx"   )[,1:4]%>%
#   StructureData()

#Ryedale
RyedaleDATA <-  read_excel("Ryedale FOI 4597.xlsx")[,1:4]%>%
  StructureData(2:6)

#Crave they sent full addresses by mistake I'll do a temporary fix
CravenDATA <- read_excel("Craven Discounts.xlsx" ) %>%
  setNames(make.names(names(.))) %>%
  mutate(Postcode = str_split(Full.Property.Address, "(,)(?!.*,)", simplify = T)[,2] %>% 
           gsub(" ", "", .)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=Discount.Type.Description, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData(c(2:5,7))

#Redcar and cleveland

RedcarDATA <-  read_excel("Redcar 0614 attachment 1.xlsx")[,1:4]%>%
  StructureData(2:10)

@@

STynesideDATA <- read_excel("FOI 17.18456 - South Tyneside Discounts.xlsx", sheet=1)[,c(1,4:6)] %>%
    StructureData(c(32:35,38))

@@

##Northumberland

```{r}
NorthumberlandDATA <- read_excel("FOI 2762 data NorthumberlandDiscounts.xlsx", sheet=1)%>% .[,1:4] %>%
    StructureData(2:7) %>%
  #The LAD code is wrong for some reason
  mutate(LAD11CD = "E06000057")

##Durham
```{r}

DurhamDATA <- read_excel("County DurhamDiscountsLSOA.XLSX" , sheet=1) %>% .[,c(1,4:6)] %>%
    StructureData()

  DarlingtonDATA <- read_excel("Darlington DBC-0809-17.xlsx" , sheet=1) %>% .[,1:4] %>%
    StructureData()

  HartlepoolDATA <- read_csv("FOI 7942 HartlepoolDiscountsLSOA.csv") %>% .[,1:4] %>%
    StructureData(2:7)

@@

#It seems Conwy really is this short on the discounts  
ConwyDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
  rename(Postcode = geo_postcode) %>%
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData(lowuse = c(2,4))

DenbigshireDATA <- read_excel("FOI 2503 DenbighshireDiscountsLSOA.xlsx" , sheet=1)%>% .[,1:4] %>%
    StructureData(8:9)

WrexhamDATA <- read_csv("WrexhamDiscountsLSOA.csv" )%>% .[,1:4] %>%
    StructureData(2:5)

#Pembrokeshire didn't send all the data
PembrokeshireDATA <- read_excel("Copy of PembrokeshireDiscountsLSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
    StructureData(3)

FlintshireDATA <- read_excel("FOI R014329 FlintshireDiscounts LSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
    StructureData()

@@

#number of LUPS and Total Homes
ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  filter(!is.na(LAD11NM)) %>%
  summarise(
           TotalLads = length(ls(pattern = "DATA", envir = globalenv())), #bits of other LADS cause the number to be higher than reality so the ls function is used again
           LowUse = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           PercHomes = Homes/sum(EW2$Homes),
           Population = sum(Pop, na.rm= T),
           Poperc = Population/sum(EW2$Pop))

@@

z<- MakeLeaflet(DurhamDATA)
z
# 
setwd(basewd)
 saveWidget(z, file=file.path(basewd, "RBKC&Westminster.html"), selfcontained = TRUE )

@@

PlotMap(BexleyLONDATA)

z <-ChelseaLONDATA %>% 
  filter(LAD11CD =="E09000020") %>% 
  bind_rows(WestminsterLONDATA) %>%
  MakeLeaflet()

@@

#Repeat excluding all the properties classed as other
setwd(basewd)
BootStrapRESExO <-LoadAddDistribCompare("BootStrapRESExO.rds", 
                                         PropertyTypes = c("D", "S", "T", "F"))
# 
# BootStrapRESExOA <-LoadAddDistribCompare("BootStrapRESExOA.rds", type = "A", 
#                                          PropertyTypes = c("D", "S", "T", "F"))
# 
# BootStrapRESExOB <-LoadAddDistribCompare("BootStrapRESExOB.rds", type = "B", 
#                                          PropertyTypes = c("D", "S", "T", "F"))

@@

#saveRDS(BootStrapRESExO, file = "BootStrapRESExO.rds")

@@

@@

```{r}
test <- BootStrapRESExO$WestminsterLON%>% 
  group_by(class) %>%
  summarise_all(funs(mean))

test2 <- test %>%
  select(-class) %>%
  summarise_all(funs(sum)) %>%
  mutate(LowUseValue = LowUseValue/1e9)

@@

@@

@@

@@

@@

#Create the extent of deprivation of the LUPs
LUPdepExt <- ls(pattern = "DATA") %>% map_dbl(~{
df <- get(.x)
test <- df %>% 
  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))

@@

@@

#Model

```{r}
LADprice <- prices %>%
  filter(X5!= "O") %>%
  group_by(Admin_district_code) %>%
summarise(price = mean(X2)) %>%
  mutate(meandiff = price-mean(price),
         pricepercent = percent_rank(price))

ModelMe <- Combine1ExO2 %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  #filter out wales
  filter(!grepl("W", LAD11CD))%>%
  select(LAD, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value, pricepercent) %>%
  mutate(Reference = as.factor(absdiff>0) ) %>%
  #scaled so that the binomial can be interpreted
  mutate(pricepercent = scale(pricepercent),
         LUPdepExt = scale(LUPdepExt),
         maxPerc = scale(maxPerc))

#This uses the local mean so that has to be run first before the code works
# ModelMe <- Combine1ExO2 %>%
#   left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
#   #filter out wales
#   filter(!grepl("W", LAD11CD))%>%
#   select(LAD11NM, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value,  LAD11CD) %>%
#   mutate(outcome = LUPdepExt>Extent)  %>% 
#   left_join(LocalMean, by = "LAD11CD") %>%
#   left_join(LADprice, by = c("LAD11CD"="Admin_district_code")) %>%
#   mutate(priceRatio = (price/LocalMean)) %>%
#   mutate(LUPdepExt.Extent = LUPdepExt-Extent, price.LocalMean = price-LocalMean ) %>%
#   #make the Reference column properly
#   mutate(Reference = as.factor(absdiff>0) ) %>%
#   #scaled so that the binomial can be interpreted
#   mutate(pricepercent = scale(pricepercent),
#          LUPdepExt = scale(LUPdepExt),
#          maxPerc = scale(maxPerc),
#          priceRatio = scale(priceRatio))

ModelMe %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = outcome)) +
  geom_jitter()

library(rpart)
library(caret)

#classification
#three models
svm.model <- svm(Reference~ pricepercent +LUPdepExt+ maxPerc, ModelMe)
rpart.model <- rpart(Reference ~pricepercent +LUPdepExt+ maxPerc, ModelMe)
Binom <- glm(Reference~ LUPdepExt + maxPerc+ pricepercent, family=binomial(link='logit'),data=ModelMe)

linear.model <- lm(absdiff~ LUPdepExt + maxPerc+ pricepercent,data=ModelMe)

confusionMatrix(predict(svm.model, ModelMe, type = "class"), ModelMe$Reference) %>% unlist
confusionMatrix( predict(rpart.model, ModelMe, type = "class"), ModelMe$Reference)
confusionMatrix(predict(Binom, ModelMe, type = "response")>0.5 , ModelMe$Reference)

predict(linear.model, ModelMe)
summary(linear.model)
```

##perform many mode resamples and plot the results

@@

set.seed(1983)
test <- 1:1000 %>% map_df(~{
TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

rpart.model2 <- rpart(Reference ~pricepercent +LUPdepExt+ maxPerc, as.data.frame(TestResample$train))

Confmat <- confusionMatrix( predict(rpart.model2, as.data.frame(TestResample$test), type = "class"), as.data.frame(TestResample$test)$Reference)

Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

}
)

test %>% ggplot(., aes(x= Accuracy)) +geom_density()

test %>%
  mutate(diff = Accuracy - AccuracyNull) %>% 
  ggplot(., aes(x= diff)) +geom_density()

t.test(test$Accuracy, test$AccuracyNull, alternative = "greater")

set.seed(1983)
test2 <- 1:1000 %>% map_df(~{
  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

  model <- svm(Reference ~pricepercent +LUPdepExt+ maxPerc, as.data.frame(TestResample$train))

  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "class"),
                              as.data.frame(TestResample$test)$Reference)

  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

}
)

test2 %>% ggplot(., aes(x= Accuracy)) +geom_density()

test2 %>%
  mutate(diff = Accuracy - AccuracyNull) %>% 
  ggplot(., aes(x= diff)) +geom_density()

t.test(test2$Accuracy, test2$AccuracyNull, alternative = "greater")

#binom

set.seed(1983)
test3 <- 1:1000 %>% map_df(~{
  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

  model <- glm(Reference~ LUPdepExt + maxPerc+ pricepercent, 
               family=binomial(link='logit'),
               as.data.frame(TestResample$train))

  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
                              as.data.frame(TestResample$test)$Reference)

  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

}
)

test3 %>% ggplot(., aes(x= Accuracy)) +geom_density()

test3 %>%
  mutate(diff = Accuracy - AccuracyNull) %>% 
  ggplot(., aes(x= diff)) +geom_density()

t.test(test3$Accuracy, test3$AccuracyNull, alternative = "greater")

# 
# set.seed(1983)
# test4 <- 1:1000 %>% map_df(~{
#   TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
# 
#   model <- glm(Reference~ LUPdepExt + maxPerc+ priceRatio, 
#                family=binomial(link='logit'),
#                as.data.frame(TestResample$train))
# 
#   Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
#                               as.data.frame(TestResample$test)$Reference) 
# 
#   Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
#           Confmat$byClass %>% as.matrix %>%t %>% data.frame,
#           coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
#   mutate(ID = .x)
# 
# }
# )
# 
# test4 %>% ggplot(., aes(x= Accuracy)) +geom_density()
# 
# test4 %>%
#   mutate(diff = Accuracy - AccuracyNull) %>% 
#   ggplot(., aes(x= diff)) +geom_density()
# 
# t.test(test4$Accuracy, test4$AccuracyNull, alternative = "greater")
# 
# 
# t.test(test3$Accuracy- test3$AccuracyNull, test4$Accuracy - test4$AccuracyNull, alternative = "greater")

@@
